paper

### 2019-01-11 Report/paper.tex
push interactive report noteboo and final report

\begin{itemize}
\item
  We used \emph{beautiful soup} and \emph{string} libraries to only keep
  sections of the text that we needed and remove special characters.
\item
  We applied \textbf{\emph{regular expression}} to remove numbers
  because numbers were not important for our analysis.
\item
  We put all words to lower case
\item
  We removed words that were connecting parts of a sentence rather than
  showing subjects, objects or intent (\textbf{\emph{stopwords}}). For
  the purpose of this task these words were not important and were only
  going to increase the bag of words length
\item
  In some methods we applied \textbf{\emph{lemmatization}} and
  \textbf{\emph{stemming}} to the words. In other methods we did not
  because we implement a mapping with \textbf{\emph{GloVe}} vocabulary
  instead, which we will explain later on.
\end{itemize}

@@

For the Keywords extraction we used three methods : The first one is a
trivial approach that consists of searching in the pdf itself for
keywords and extract them, this method is the most accurate but we found
out that for 492 papers we had no keywords included. So we deciced to
use other two methods for keywords extraction, namely one based on
\textbf{\emph{TF-IDF}} and a second one based on \textbf{\emph{Rake}}.
\textbf{\emph{TF-IDF}} is one of the most popular term-weighting schemes
today, in information retrieval, tf--idf or TFIDF, short for term
frequency--inverse document frequency, is a numerical statistic that is
intended to reflect how important a word is to a document in a
collection or corpus. It is often used as a weighting factor in searches
of information retrieval, text mining, and user modeling. The tf--idf
value increases proportionally to the number of times a word appears in
the document and is offset by the number of documents in the corpus that
contain the word, which helps to adjust for the fact that some words
appear more frequently in general \cite{Tf-idf}. With TF-IDF we sorted
for each document the words with the highest score and then selected the
7 first words of each document.

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_48_0.png}\end{center}
        \caption{Largest Component of the multiple collaboration co-authorship graph}
        \label{author_collab_large}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{unigraph}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_57_0.png}\end{center}
        \caption{Global spread of community. Size of dot represent number of participants from each institution}
        \label{global_com}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_59_0.png}\end{center}
        \caption{Number of Contributiors by country, excluding the US}
        \label{figrep}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_61_0.png}\end{center}
        \caption{Collaboration between countries excluding the US}
        \label{figcollab}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_63_0.png}\end{center}
        \caption{Subcommunities via normalized cuts in largest component of co-authorship graph}
        \label{normalized}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
        \caption{Subcommunities by participation in CSCL. Blue: no participation in main components of CSCL. Red and orange each mark participation in one of the two main components of CSCL}
        \label{CSCL_components}
    \end{figure}

@@

The fact that normalized graph cuts will split the community into three
prompted further investigation. As will be discussed in the next
section, the graph of authors that participanted in CSCL yields two
large connected components. By coloring the authors contained in the two
CSCL components with different colors, and authors in neither with a
third color, we found a similar partitioning of the graph, as can be
observed in figure \ref{CSCL_components}. This is somewhat trivial, as
the graph is built based on collaboration in these conferences. However,
the analysis of nationalities present in the graph yielded an
interesting results. All Asian participants from nations other than
Singapore are contained in the same cluster. We also observed that one
of the CSCL clusters is closer to the group of ICLS-only participants
than the other. Additionaly, through normalized splits, we found that
the section of the normalized cut containing ICLS only authors is
overwhelmingly American.

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
        \caption{Keywords of the blue community}
        \label{c1}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_67_0.png}\end{center}
        \caption{Keywords of the red community}
        \label{c2}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
        \caption{Keywords of the orange community}
        \label{c3}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_71_0.png}\end{center}
        \caption{Movement of participants across institutions}
        \label{fig_move}
    \end{figure}

@@

We observe a growth of the number of participants over the years, and by
building co-authorship graphs for each year of the conference, we
observed that the density and clustering coefficient of the graph
indicate a steady decrease, while the diameter and average shortest path
length tend to increase. This hints that the community is attracting new
member that do not collaborate with the established group of
participants. But, as the years 2018 shows a massive increase of
participation, in number of participants and number of institutions
represented, as well as a large decrease in density of the graph --which
is reduced by more than half from the previous ICLS conference-- it is
impossible to draw any statisically significant conclusion.

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_74_0.png}\end{center}
        \caption{Distribution of the number of referenced documents belonging to each year}
        \label{count_ref_docs}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_76_0.png}\end{center}
        \caption{Distribution of the 100 most referenced documents belonging to each year}
        \label{fig7}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_79_0.png}\end{center}
        \caption{In-degree count for each document}
        \label{indegree}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_81_0.png}\end{center}
        \caption{Count of documents cited together}
        \label{fig8}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_83_0.png}\end{center}
        \caption{Table of the documents belonging to the same clusters}
        \label{fig9}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_85_0.png}\end{center}
        \caption{Fully connected references graph}
        \label{fig12}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_89_0.png}\end{center}
        \caption{Giant component graph}
        \label{fig15}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_90_0.png}\end{center}
        \caption{Documents belonging to the giant component}
        \label{fig10}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_92_0.png}\end{center}
        \caption{Documents in conferences belonging to the same clusters}
        \label{fig11}
    \end{figure}

>>>>

\begin{itemize}
\item
  We used \emph{beautiful soup} and \emph{string} libraries to only keep
  sections of the text that we needed and remove special characters.
\item
  We applied \textbf{\emph{regular expression}} to remove numbers
  because numbers were not important for our analysis.
\item
  We put all words to lower case.
\item
  We removed words that were connecting parts of a sentence rather than
  showing subjects, objects or intent (\textbf{\emph{stopwords}}). For
  the purpose of this task these words were not important and were only
  going to increase the bag of words length.
\item
  In some methods we applied \textbf{\emph{lemmatization}} and
  \textbf{\emph{stemming}} to the words. In other methods we did not
  because we implement a mapping with \textbf{\emph{GloVe}} vocabulary
  instead, which we will explain later on.
\end{itemize}

@@

For the Keywords extraction we used three methods : The first one is a
trivial approach that consists of searching in the pdf itself for
keywords and extract them, this method is the most accurate but we found
out that 492 papers had no keywords included. So we deciced to use two
other methods for keywords extraction, namely one based on
\textbf{\emph{TF-IDF}} and a second one based on \textbf{\emph{Rake}}.

\textbf{\emph{TF-IDF}} is one of the most popular term-weighting schemes
today, in information retrieval, tf--idf or TFIDF, short for term
frequency--inverse document frequency, is a numerical statistic that is
intended to reflect how important a word is to a document in a
collection or corpus. It is often used as a weighting factor in searches
of information retrieval, text mining, and user modeling. The tf--idf
value increases proportionally to the number of times a word appears in
the document and is offset by the number of documents in the corpus that
contain the word, which helps to adjust for the fact that some words
appear more frequently in general \cite{Tf-idf}. With TF-IDF we sorted
for each document the words with the highest score and then selected the
7 first words of each document.

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_48_0.png}\end{center}
        \caption{Largest component of the multiple collaboration co-authorship graph}
        \label{author_collab_large}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
        \caption{Main component of institution collaboration graph}
        \label{unigraph}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_58_0.png}\end{center}
        \caption{Global spread of community. Size of dot represents the number of participants from each institution}
        \label{global_com}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_60_0.png}\end{center}
        \caption{Number of participants by country, excluding the US}
        \label{figrep}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_62_0.png}\end{center}
        \caption{Collaboration between countries excluding the US}
        \label{figcollab}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
        \caption{Subcommunities via normalized cuts in largest component of co-authorship graph}
        \label{normalized}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
        \caption{Subcommunities by participation in CSCL. Blue: no participation in main components of CSCL. Red and orange each mark participation in one of the two main components of CSCL}
        \label{CSCL_components}
    \end{figure}

@@

The fact that normalized graph cuts will split the community into three
prompted further investigation. As will be discussed in the next
section, the graph of authors that participanted in CSCL yields two
large connected components. By coloring the authors contained in the two
CSCL components with different colors, and authors in neither with a
third color, we found a similar partitioning of the graph, as can be
observed in figure \ref{CSCL_components}. This is somewhat trivial, as
the graph is built based on collaboration in these conferences. However,
the analysis of nationalities present in the graph yielded an
interesting results. All Asian participants from nations other than
Singapore are contained in the same cluster. We also observed that one
of the CSCL clusters (orange in \ref{CSCL_components}) is closer to the
group of ICLS-only participants than the other (red component).
Additionaly, through normalized splits, we found that the section of the
normalized cut containing mostly ICLS only authors (blue in
\ref{normalized}) is overwhelmingly American.

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
        \caption{Keywords of the blue community}
        \label{c1}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_69_0.png}\end{center}
        \caption{Keywords of the orange community}
        \label{c2}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_70_0.png}\end{center}
        \caption{Keywords of the red community}
        \label{c3}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_73_0.png}\end{center}
        \caption{Movement of participants across institutions}
        \label{fig_move}
    \end{figure}

@@

We observe a growth of the number of participants over the years, and by
building co-authorship graphs for each year of the conference, we
observed that the density and clustering coefficient of the graph
indicate a steady decrease, while the diameter and average shortest path
length tend to increase. This suggests that the community is attracting
new members that do not collaborate with the established group of
participants. But, as the years 2018 shows a massive increase of
participation, in number of participants and number of institutions
represented, as well as a large decrease in density of the graph --which
is reduced by more than half from the previous ICLS conference-- it is
impossible to draw any statisically significant conclusion.

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_76_0.png}\end{center}
        \caption{Distribution of the number of referenced documents belonging to each year}
        \label{count_ref_docs}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_78_0.png}\end{center}
        \caption{Distribution of the 100 most referenced documents belonging to each year}
        \label{fig7}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_81_0.png}\end{center}
        \caption{In-degree count for each document}
        \label{indegree}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_83_0.png}\end{center}
        \caption{Count of documents cited together}
        \label{fig8}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_85_0.png}\end{center}
        \caption{Table of the documents belonging to the same clusters}
        \label{fig9}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_87_0.png}\end{center}
        \caption{Fully connected references graph}
        \label{fig12}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_91_0.png}\end{center}
        \caption{Giant component graph}
        \label{fig15}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_92_0.png}\end{center}
        \caption{Documents belonging to the giant component}
        \label{fig10}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_94_0.png}\end{center}
        \caption{Documents in conferences belonging to the same clusters}
        \label{fig11}
    \end{figure}
